Insights Into Computational Reproducibility in Plant Pathology and a Way Forward

### 2021-06-11 analysis/paper/paper.Rmd
Rework table displays and add new table for scoring criteria

import_notes() %>%
  tabyl(journal) %>%
  select(-percent) %>%
  flextable() %>%
  autofit()
```

@@

```{r software_avail, tab.id="sa", tab.cap="Article ratings for software availability where '0', not available or not mentioned in publication to '3', preferably open source and freely available.", echo=FALSE, message=FALSE, warning=FALSE}
import_notes() %>%
  tabyl(software_avail) %>%
  adorn_pct_formatting() %>% 
  select(-percent) %>% 
  rename(`software availability` = software_avail,
         percent = valid_percent) %>% 
  flextable() %>%
  autofit()
```

@@

```{r software_cite, tab.id="sc", tab.cap="Article ratings for software citations where '0', not specified or mentioned in publication to '3', fully cited with proper version numbers and all procedures detailed.", echo=FALSE, message=FALSE, warning=FALSE}
import_notes() %>%
  tabyl(software_cite) %>%
  adorn_pct_formatting() %>% 
  select(-percent) %>% 
  rename(`software citation` = software_cite,
         percent = valid_percent) %>% 
  flextable() %>%
  autofit()
```

@@

```{r data_available, tab.id="da", tab.cap="Article ratings for data availability where '0', not specified or mentioned in publication to '3', Freely available online to anonymous users for foreseeable future (*e.g.*, archived using Zenodo, dataverse or university library or some other proper archiving system).", echo=FALSE, message=FALSE, warning=FALSE}
import_notes() %>%
  tabyl(data_avail) %>%
  adorn_pct_formatting() %>% 
  select(-percent) %>% 
  rename(`data availability` = data_avail,
         percent = valid_percent) %>% 
  flextable() %>%
  autofit()
```

@@

```{r software_used, tab.id="su", tab.cap="Tally of reproducibility scores where 0 is not reproducible and 12 is fully reproducible, *e.g.*, all software cited, software used are freely available to anyone, computational methods (statistical analysis or other computational code) are freely available for download and use, and raw data are available for download and use.", echo=FALSE, message=FALSE, warning=FALSE}
library("tidyr")

@@

```{r reproducibility_score, tab.id="reproducibility", tab.cap="Tally of reproducibility scores where 0 is not reproducible and 12 is fully reproducible, *e.g.*, all software cited, software used are freely available to anyone, computational methods (statistical analysis or other computational code) are freely available for download and use, and raw data are available for download and use.", echo=FALSE, message=FALSE, warning=FALSE}
import_notes() %>%
  tabyl(reproducibility_score) %>%
  adorn_pct_formatting() %>%
  rename(score = reproducibility_score) %>%
  flextable() %>%
  autofit()
```

>>>>

import_notes() %>%
  tabyl(journal) %>%
  select(-percent) %>%
  rename(Journal = journal) %>% 
  flextable() %>%
  colformat_num(na_str = "NA") %>% 
  autofit()
```

@@

```{r scoring, tab.id="scoring", tab.cap ="Articles were scored in four areas for reproducibility on a scale of 0 to 3 by four independent assessors.", echo=FALSE, message=FALSE, warning=FALSE}
scoring_criteria %>% 
  rename(`Index Value` = Index.Value) %>% 
  flextable() %>% 
  colformat_num(na_str = "NA") %>% 
  set_table_properties(layout = "autofit")
```

@@

```{r software_avail, tab.id="sa", tab.cap="Article ratings for software availability where '0', not available or not mentioned in publication to '3', preferably open source and freely available.", echo=FALSE, message=FALSE, warning=FALSE}
import_notes() %>%
  tabyl(software_avail) %>%
  adorn_pct_formatting() %>% 
  select(-valid_percent) %>% 
  rename(`Software Availability` = software_avail,
         Percent = percent) %>% 
  flextable() %>%
  colformat_num(na_str = "NA") %>% 
  autofit()
```

@@

```{r software_cite, tab.id="sc", tab.cap="Article ratings for software citations where '0', not specified or mentioned in publication to '3', fully cited with proper version numbers and all procedures detailed.", echo=FALSE, message=FALSE, warning=FALSE}
import_notes() %>%
  tabyl(software_cite) %>%
  adorn_pct_formatting() %>% 
  select(-valid_percent) %>% 
  rename(`Software citation` = software_cite,
         Percent = percent) %>% 
  flextable() %>%
  colformat_num(na_str = "NA") %>% 
  autofit()
```

@@

```{r data_available, tab.id="da", tab.cap="Article ratings for data availability where '0', not specified or mentioned in publication to '3', Freely available online to anonymous users for foreseeable future (_e.g._, archived using Zenodo, dataverse or university library or some other proper archiving system).", echo=FALSE, message=FALSE, warning=FALSE}
import_notes() %>%
  tabyl(data_avail) %>%
  adorn_pct_formatting() %>% 
  select(-percent) %>% 
  rename(`Data availability` = data_avail,
         Percent = valid_percent) %>% 
  flextable() %>%
  colformat_num(na_str = "NA") %>% 
  autofit()
```

```{r software_used, tab.id="su", tab.cap="Tally of reproducibility scores where 0 is not reproducible and 12 is fully reproducible, _e.g._, all software cited, software used are freely available to anyone, computational methods (statistical analysis or other computational code) are freely available for download and use, and raw data are available for download and use.", echo=FALSE, message=FALSE, warning=FALSE}
library("tidyr")

@@

```{r reproducibility_score, tab.id="reproducibility", tab.cap="Tally of reproducibility scores where 0 is not reproducible and 12 is fully reproducible, _e.g._, all software cited, software used are freely available to anyone, computational methods (statistical analysis or other computational code) are freely available for download and use, and raw data are available for download and use.", echo=FALSE, message=FALSE, warning=FALSE}
import_notes() %>%
  tabyl(reproducibility_score) %>%
  adorn_pct_formatting() %>%
  rename(score = reproducibility_score) %>%
  flextable() %>%
  autofit()
```
